---
title: "Content"
output: rmarkdown::html_vignette
toc:
  depth: 2
vignette: >
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
  %\VignetteIndexEntry{Content}
---


## Learning material

The course content is divided in chapters: for each topic,
readers have access to course notes, sample code, online quizzes and exercises.


- [Basics of inference](https://lbelzile.github.io/math60604a/intro.html)
- [Linear regression](https://lbelzile.github.io/math60604a/linear-regression.html)
- [Generalized linear models](https://lbelzile.github.io/math60604a/generalized-linear-models.html)
- [Correlated and longitudinal data](https://lbelzile.github.io/math60604a/correlated-longitudinal-data.html)
- [Linear mixed models](https://lbelzile.github.io/math60604a/linear-mixed-models.html)
- [Survival analysis](https://lbelzile.github.io/math60604a/survival.html)
- [Likelihood](https://lbelzile.github.io/math60604a/likelihood.html)

---



## Videos and Slides

In this section you can find the links to all videos individually as well as the slides and accompanying code used in the videos.

```{r, echo=FALSE, eval=TRUE, message=FALSE}
source("get_slide_data.R")

knitr::kable(sldat)
```


## Exercises

```{r, echo=FALSE, eval=TRUE, message=FALSE}
source("get_exercise_data.R")
knitr::kable(exdat, row.names = FALSE)
```


## Code

You can run the following code excerpts on your own computer.

```{r, echo=FALSE, eval=FALSE, message=FALSE}
source("get_demo_data.R")

kable(subset(cddat, select = c("Topic", "Demo", "R", "SAS")), row.names = FALSE)
```

## Exercises

```{r, echo=FALSE, eval=FALSE, message=FALSE}
source("get_exercise_data.R")

kable(exdat, row.names = FALSE)
```
